\documentclass{letter}

%\usepackage[top=40mm, bottom=40mm, left=30mm, right=16mm]{geometry}
\usepackage[top=40mm]{geometry}

\signature{Yuan-Fang Li}
\address{School of ITEE\\The University of Queensland}

\begin{document}

\begin{letter}{Editors, Special Issue on Semantic Web Dynamics\\Journal of Web Semantics}

\opening{Dear Editors:}

I am writing in response to the call for papers of the Special Issue
on Semantic Web Dynamics in the Journal of Web Semantics. With this
letter I submit a manuscript titled ``An Ontology-driven
Architecture for Extensible Scientific Data Management Systems'' for
your consideration.

This paper describes our work in designing an ontology-driven
architecture for developing extensible data management systems
to support dynamic domain models. We also describe our
efforts in developing the PODD system based on this
architecture as a demonstration of the practicability of the
proposed architecture.

Please note that this manuscript is based on an extended
abstract accepted at the 12th International Conference on
Asian Digital Libraries (ICADL 2010), titled ``PODD: An
Ontology-driven Data Repository for Collaborative
Phenomics Research''. Compared to the extended abstract,
the current manuscript contains substantial new contents,
including:

\begin{itemize}
\item A more comprehensive survey of relevant works.

\item The proposal of the domain-independent
ontology-driven architecture for developing
data management systems.

\item A more detailed description of the base ontology
and its roles in the data management system.

\item The separation of the domain-independent
base ontology and the phenomics-specific ontology
and the description of how they are integrated in
the PODD system.

\item A more detailed description of the PODD system.
\end{itemize}

Thank you in advance for reviewing our paper. Please
do not hesitate to contact me should you have any
queries.

\closing{Sincerely,}

\end{letter}
\end{document}
